MVC is an excellent means of separating presentation and interaction from system data it. \par

\textbf{Modular.} The code becomes modular as there is separation of concerns, views can be developed independently of the database.\par

\textbf{Maintainable.} The code is modular and better structured, therefore easier to understand because the code is separated into modules,
bugs may be constrained to a particular module rather than entire system. This then speaks to testing as
it becomes easier to test as well since the code is self contained. \par

\textbf{Parallel development by different entities.} The code is not coupled, therefore modules can be developed in parallel, UI can
be designed, the business logic developed and the database created all in parallel. \par

\textbf{Easy Interface updates.} Views can be created without interference of the current system and just replace the
old ones since they aren't closely coupled. \par

\textbf{Pluggable components.} This ties into updates, because modules are loosely coupled and foster separation of responsibilities, components are easy to plug in to the system. More specifically controllers who control the logic are easier to plugin as
the layers for the view and database stay the same but only the logic changes.\par

\textbf{Reusable.}The code is self-contained and responsible for itself, therefore elements such as UI components
which may contain some functionality within it such as validation may be reused e.g. buttons, text fields
